---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# sp_df

In `sp_df` we can store the `Spatial*` (without the DataFrame) geometry in a special column. 

```{r}
geocol <- sp_df(wrld_simpl)
geocol %>% dplyr::select(NAME, Spatial_)
```

Note that this approach can be easily applied with WKT or WKB, it's just a fair bit of extra work to do the type conversion when needed. Note that, R has a `raw` type that seamlessly handles WKB from many DBs, and the `wkb` package can read it, likewise with `rgeos::readWKT` and `rgeos::writeWKT`. (See this in action in [manifoldr](https://github.com/mdsumner/manifoldr).)

## Questions on sp_df


Can we use mutate with the as coercion? 

```{r}
spdf <- sp_df(wrld_simpl)
## this doesn't work
#spdf %>% mutate(Spatial_ = as(Spatial_, "SpatialLines"))
spdf$Spatial_ <- as(spdf$Spatial_, "SpatialLines")
```

How to apply this, as an extra class? Note that geom_polygon in gggeom does not survive filter since the class attribute is lost. 
